TrueGrid: Code the Table, Tabulate the Data

### 2016-04-19 true-grid/paper_SEMS16.tex
Fixed leftpad

\begin{figure}[t]
\begin{minipage}{0.6\linewidth}
\begin{lstlisting}
function leftpad(str, len, ch) {
  str = String(str);
  var i = -1;
  if (!ch && ch !== 0) ch = ' ';
  len = len - str.length;
  while (++i < len) {
    str = ch + str;
  }
  return str;
}
\end{lstlisting}
\end{minipage}
\begin{minipage}{0.4\linewidth}
\centering
\sffamily
\begin{tabular}{|c|c|m{0.5cm}|p{0.5cm}|c|}\hline
function & 0 & 1 & 2 & Result \\\hline\hline
leftpad & "foo" & 5 &  & "  foo" \\\hline
leftpad & "foobar" & 6 & & "foobar" \\\hline
leftpad & 1 & 2 & 3 & "01"\\\hline
\end{tabular}
\end{minipage}
\caption{Exploring function behavior using TrueGrid}
\label{FIG:leftpad}
\end{figure}

>>>>

\begin{figure}[t]
\begin{minipage}{0.6\linewidth}
\begin{lstlisting}
function leftpad(str, len, ch) {
  str = String(str);
  var i = -1;
  if (!ch && ch !== 0) ch = ' ';
  len = len - str.length;
  while (++i < len) {
    str = ch + str;
  }
  return str;
}
\end{lstlisting}
\end{minipage}
\begin{minipage}{0.4\linewidth}
\centering
\sffamily
\begin{tabular}{|c|c|m{0.5cm}|p{0.5cm}|c|}\hline
function & 0 & 1 & 2 & Result \\\hline\hline
leftpad & "foo" & 5 &  & "  foo" \\\hline
leftpad & "foobar" & 6 & & "foobar" \\\hline
leftpad & 1 & 2 & 0 & "01"\\\hline
\end{tabular}
\end{minipage}
\caption{Exploring function behavior using TrueGrid}
\label{FIG:leftpad}
\end{figure}
